Preprocessing

### 2023-08-29 analysis/preprocessing.Rmd
Update preprocessing.Rmd

```{r setup, include=FALSE}
library(tidyverse) # for various tasks including munging and plotting
library(here) # for easier file path access
library(tidylog) # for inline programming reporting
library(assertthat) # for testing
`%notin%` <- Negate(`%in%`) # for identifying when values are not in a vector of expected values
```

>>>>

```{r setup, include=FALSE}
library(tidyverse) # for various tasks including munging and plotting
library(here) # for easier file path access
library(tidylog) # for inline programming reporting
library(assertthat) # for testing
source(here('analysis','functions.R')) # load custom functions
```
